---
title: "tazoot_swap_chance"
author: Jenny Motzer
output: github_document
date: "2025-06-10"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
suppressPackageStartupMessages(library(tidyverse))
library(ez)
library(foreach)
library(kableExtra)
library(ggplot2)
library(dplyr)
library(ggpubr)
library(lsr)
library(report)
library(purrr)
library(tidyr)
library(broom)
library(rempsyc) # for t-tests in nice tables
knitr::opts_chunk$set(echo = TRUE)

#### anova setup #### 
options(contrasts=c("contr.sum","contr.poly"))

#### load data #### 
wd <- getwd()
analysisName = 'tazoot_twoIncorrect_errSwapAcc'
dataName <- sprintf("/Users/jennymotzer/Documents/GitHub/ZOOT/stats/%s.csv", analysisName)
data <- read.csv(dataName)
data_clean <- data[!is.nan(data$twoIncorrect), ]
data <- data_clean
#### Change to categorical vars ####
data$SID <- factor(data$SID)
data$targetContrast <- factor(data$targetContrast)
data$nontargetContrast <- factor(data$nontargetContrast)
data$Target <- factor(data$Target)
data$Validity <- factor(data$Validity)

### Plotting setup #### 
colors = c("#F8A299","#CCCCCC","#98E6A1")
attComparison <- list( c("1","3"), c("1","2"), c("2","3") )

significance <- list(cutpoints = c(0, 0.0001, 0.001, 0.01, 0.05, Inf),
symbols = c("****", "***", "**", "*", "ns"))
```

```{r swap V}
d <- data %>% filter(Validity == 1)
t.test(d$twoIncorrect, mu=50)  %>% report %>%
  as.data.frame -> stats.table
my_table <- nice_table(stats.table, report = "t.test", title = "tazoot swap chance")
my_table
```
report(swap)
```

# V
```{r swap V}
d <- data 
dt <- d %>% filter(Validity == 1)
swap_V <-t.test(dt$twoIncorrect, mu=50) 
report(swap_V)
```
# N
```{r swap N}
d <- data 
dt <- d %>% filter(Validity == 3)
swap_N <-t.test(dt$twoIncorrect, mu=50) 
report(swap_N)
```
# I
```{r swap I}
d <- data 
dt <- d %>% filter(Validity == 2)
swap_I <-t.test(dt$twoIncorrect, mu=50) 
report(swap_I)
```

# T1
```{r swap T1}
d <- data 
dt <- d %>% filter(Target == 1)
swap_T1 <-t.test(dt$twoIncorrect, mu=50) 
report(swap_T1)
```
## V
```{r swap T1 V}
d <- data 
dt <- d %>% filter(Target==1, Validity == 1)
swap_T1V <-t.test(dt$twoIncorrect, mu=50) 
report(swap_T1V)
```
## N
```{r swap T1 N}
d <- data 
dt <- d %>% filter(Target==1, Validity == 3)
swap_T1N <-t.test(dt$twoIncorrect, mu=50) 
report(swap_T1N)
```
## I
```{r swap T1 I}
d <- data 
dt <- d %>% filter(Target==1, Validity == 2)
swap_T1I <-t.test(dt$twoIncorrect, mu=50) 
report(swap_T1I)
```
# T2
```{r swap T2}
d <- data 
dt <- d %>% filter(Target == 2)
swap_T2 <-t.test(dt$twoIncorrect, mu=50) 
report(swap_T2)
```
## V
```{r swap T2 V}
d <- data 
dt <- d %>% filter(Target==2, Validity == 1)
swap_T2V <-t.test(dt$twoIncorrect, mu=50) 
report(swap_T2V)
```
## N
```{r swap T2 N}
d <- data 
dt <- d %>% filter(Target==2, Validity == 3)
swap_T2N <-t.test(dt$twoIncorrect, mu=50) 
report(swap_T2N)
```
## I
```{r swap T2 I}
d <- data 
dt <- d %>% filter(Target==2, Validity == 2)
swap_T2I <-t.test(dt$twoIncorrect, mu=50) 
report(swap_T2I)
```
# TP 
```{r swap TP}
d <- data 
dt <- d %>% filter(targetContrast == 1)
swap_TP <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TP)
```
## T1
```{r swap TP T1}
d <- data 
dt <- d %>% filter(targetContrast == 1, Target==1)
swap_TPT1 <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TPT1)
```
## T2
```{r swap TP T2}
d <- data 
dt <- d %>% filter(targetContrast == 1, Target==2)
swap_TPT2 <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TPT2)
```
## V
```{r swap TP V}
d <- data 
dt <- d %>% filter(targetContrast == 1, Validity==1)
swap_TPV <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TPV)
```
## N
```{r swap TP N}
d <- data 
dt <- d %>% filter(targetContrast == 1, Validity==3)
swap_TPN <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TPN)
```
## I 
```{r swap TP I}
d <- data 
dt <- d %>% filter(targetContrast == 1, Validity==2)
swap_TPI <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TPI)
```
## T1 V
```{r swap TP T1 V}
d <- data 
dt <- d %>% filter(targetContrast == 1, Validity==1, Target==1)
swap_TPT1V <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TPT1V)
```
## T1 N
```{r swap TP T1 N}
d <- data 
dt <- d %>% filter(targetContrast == 1, Validity==3, Target==1)
swap_TPT1N <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TPT1N)
```
## T1 I
```{r swap TP T1 I}
d <- data 
dt <- d %>% filter(targetContrast == 1, Validity==2, Target==1)
swap_TPT1I <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TPT1I)
```
## T2 V
```{r swap TP T2 V}
d <- data 
dt <- d %>% filter(targetContrast == 1, Validity==1, Target==2)
swap_TPT2V <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TPT2V)
```
## T2 N
```{r swap TP T2 N}
d <- data 
dt <- d %>% filter(targetContrast == 1, Validity==3, Target==2)
swap_TPT2N <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TPT2N)
```
## T2 I
```{r swap TP T2 I}
d <- data 
dt <- d %>% filter(targetContrast == 1, Validity==2, Target==2)
swap_TPT2I <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TPT2I)
```

# TA 
```{r swap TA}
d <- data 
dt <- d %>% filter(targetContrast == 0)
swap_TA <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TA)
```
## T1
```{r swap TA T1}
d <- data 
dt <- d %>% filter(targetContrast == 0, Target==1)
swap_TAT1 <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TAT1)
```
## T2
```{r swap TA T2}
d <- data 
dt <- d %>% filter(targetContrast == 0, Target==2)
swap_TAT2 <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TAT2)
```
## V
```{r swap TA V}
d <- data 
dt <- d %>% filter(targetContrast == 0, Validity==1)
swap_TAV <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TAV)
```
## N
```{r swap TA N}
d <- data 
dt <- d %>% filter(targetContrast == 0, Validity==3)
swap_TAN <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TAN)
```
## I 
```{r swap TA I}
d <- data 
dt <- d %>% filter(targetContrast == 0, Validity==2)
swap_TAI <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TAI)
```
## T1 V
```{r swap TA T1 V}
d <- data 
dt <- d %>% filter(targetContrast == 0, Validity==1, Target==1)
swap_TAT1V <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TAT1V)
```
## T1 N
```{r swap TA T1 N}
d <- data 
dt <- d %>% filter(targetContrast == 0, Validity==3, Target==1)
swap_TAT1N <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TAT1N)
```
## T1 I
```{r swap TA T1 I}
d <- data 
dt <- d %>% filter(targetContrast == 0, Validity==2, Target==1)
swap_TAT1I <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TAT1I)
```
## T2 V
```{r swap TA T2 V}
d <- data 
dt <- d %>% filter(targetContrast == 0, Validity==1, Target==2)
swap_TAT2V <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TAT2V)
```
## T2 N
```{r swap TA T2 N}
d <- data 
dt <- d %>% filter(targetContrast == 0, Validity==3, Target==2)
swap_TAT2N <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TAT2N)
```
## T2 I
```{r swap TA T2 I}
d <- data 
dt <- d %>% filter(targetContrast == 0, Validity==2, Target==2)
swap_TAT2I <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TAT2I)
```

#TPNP
```{r swap TPNP}
d <- data 
dt <- d %>% filter(targetContrast == 1, nontargetContrast == 1)
swap_TPNP <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TPNP)
```
## T1
```{r swap TPNP T1}
d <- data 
dt <- d %>% filter(targetContrast == 1, nontargetContrast == 1, Target==1)
swap_TPNPT1 <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TPNPT1)
```
## T2
```{r swap TPNP T2}
d <- data 
dt <- d %>% filter(targetContrast == 1, nontargetContrast == 1, Target==2)
swap_TPNPT2 <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TPNPT2)
```
## V
```{r swap TPNP V}
d <- data 
dt <- d %>% filter(targetContrast == 1, nontargetContrast == 1, Validity==1)
swap_TPNPV <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TPNPV)
```
## N
```{r swap TPNP N}
d <- data 
dt <- d %>% filter(targetContrast == 1, nontargetContrast == 1, Validity==3)
swap_TPNPN <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TPNPN)
```
## I 
```{r swap TPNP I}
d <- data 
dt <- d %>% filter(targetContrast == 1, nontargetContrast == 1, Validity==2)
swap_TPNPI <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TPNPI)
```
## T1 V
```{r swap TPNP T1 V}
d <- data 
dt <- d %>% filter(targetContrast == 1, nontargetContrast == 1, Validity==1, Target==1)
swap_TPNPT1V <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TPNPT1V)
```
## T1 N
```{r swap TPNP T1 N}
d <- data 
dt <- d %>% filter(targetContrast == 1, nontargetContrast == 1, Validity==3, Target==1)
swap_TPNPT1N <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TPNPT1N)
```
## T1 I
```{r swap TPNP T1 I}
d <- data 
dt <- d %>% filter(targetContrast == 1, nontargetContrast == 1, Validity==2, Target==1)
swap_TPNPT1I <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TPNPT1I)
```
## T2 V
```{r swap TPNP T2 V}
d <- data 
dt <- d %>% filter(targetContrast == 1, nontargetContrast == 1, Validity==1, Target==2)
swap_TPNPT2V <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TPNPT2V)
```
## T2 N
```{r swap TPNP T2 N}
d <- data 
dt <- d %>% filter(targetContrast == 1, nontargetContrast == 1, Validity==3, Target==2)
swap_TPNPT2N <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TPNPT2N)
```
## T2 I
```{r swap TPNP T2 I}
d <- data 
dt <- d %>% filter(targetContrast == 1, nontargetContrast == 1, Validity==2, Target==2)
swap_TPNPT2I <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TPNPT2I)
```

# TPNA
```{r swap TPNA}
d <- data 
dt <- d %>% filter(targetContrast == 1, nontargetContrast == 0)
swap_TPNA <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TPNA)
```
## T1
```{r swap TPNA T1}
d <- data 
dt <- d %>% filter(targetContrast == 1, nontargetContrast == 0, Target==1)
swap_TPNAT1 <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TPNAT1)
```
## T2
```{r swap TPNA T2}
d <- data 
dt <- d %>% filter(targetContrast == 1, nontargetContrast == 0, Target==2)
swap_TPNAT2 <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TPNAT2)
```
## V
```{r swap TPNA V}
d <- data 
dt <- d %>% filter(targetContrast == 1, nontargetContrast == 0, Validity==1)
swap_TPNAV <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TPNAV)
```
## N
```{r swap TPNA N}
d <- data 
dt <- d %>% filter(targetContrast == 1, nontargetContrast == 0, Validity==3)
swap_TPNAN <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TPNAN)
```
## I 
```{r swap TPNA I}
d <- data 
dt <- d %>% filter(targetContrast == 1, nontargetContrast == 0, Validity==2)
swap_TPNAI <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TPNAI)
```
## T1 V
```{r swap TPNA T1 V}
d <- data 
dt <- d %>% filter(targetContrast == 1, nontargetContrast == 0, Validity==1, Target==1)
swap_TPNAT1V <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TPNAT1V)
```
## T1 N
```{r swap TPNA T1 N}
d <- data 
dt <- d %>% filter(targetContrast == 1, nontargetContrast == 0, Validity==3, Target==1)
swap_TPNAT1N <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TPNAT1N)
```
## T1 I
```{r swap TPNA T1 I}
d <- data 
dt <- d %>% filter(targetContrast == 1, nontargetContrast == 0, Validity==2, Target==1)
swap_TPNAT1I <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TPNAT1I)
```
## T2 V
```{r swap TPNA T2 V}
d <- data 
dt <- d %>% filter(targetContrast == 1, nontargetContrast == 0, Validity==1, Target==2)
swap_TPNAT2V <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TPNAT2V)
```
## T2 N
```{r swap TPNA T2 N}
d <- data 
dt <- d %>% filter(targetContrast == 1, nontargetContrast == 0, Validity==3, Target==2)
swap_TPNAT2N <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TPNAT2N)
```
## T2 I
```{r swap TPNA T2 I}
d <- data 
dt <- d %>% filter(targetContrast == 1, nontargetContrast == 0, Validity==2, Target==2)
swap_TPNAT2I <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TPNAT2I)
```

# TANP
```{r swap TANP}
d <- data 
dt <- d %>% filter(targetContrast == 0, nontargetContrast == 1)
swap_TANP <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TANP)
```
## T1
```{r swap TANP T1}
d <- data 
dt <- d %>% filter(targetContrast == 0, nontargetContrast == 1, Target==1)
swap_TANPT1 <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TANPT1)
```
## T2
```{r swap TANP T2}
d <- data 
dt <- d %>% filter(targetContrast == 0, nontargetContrast == 1, Target==2)
swap_TANPT2 <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TANPT2)
```
## V
```{r swap TANP V}
d <- data 
dt <- d %>% filter(targetContrast == 0, nontargetContrast == 1, Validity==1)
swap_TANPV <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TANPV)
```
## N
```{r swap TANP N}
d <- data 
dt <- d %>% filter(targetContrast == 0, nontargetContrast == 1, Validity==3)
swap_TANPN <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TANPN)
```
## I 
```{r swap TANP I}
d <- data 
dt <- d %>% filter(targetContrast == 0, nontargetContrast == 1, Validity==2)
swap_TANPI <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TANPI)
```
## T1 V
```{r swap TANP T1 V}
d <- data 
dt <- d %>% filter(targetContrast == 0, nontargetContrast == 1, Validity==1, Target==1)
swap_TANPT1V <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TANPT1V)
```
## T1 N
```{r swap TANP T1 N}
d <- data 
dt <- d %>% filter(targetContrast == 0, nontargetContrast == 1, Validity==3, Target==1)
swap_TANPT1N <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TANPT1N)
```
## T1 I
```{r swap TANP T1 I}
d <- data 
dt <- d %>% filter(targetContrast == 0, nontargetContrast == 1, Validity==2, Target==1)
swap_TANPT1I <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TANPT1I)
```
## T2 V
```{r swap TANP T2 V}
d <- data 
dt <- d %>% filter(targetContrast == 0, nontargetContrast == 1, Validity==1, Target==2)
swap_TANPT2V <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TANPT2V)
```
## T2 N
```{r swap TANP T2 N}
d <- data 
dt <- d %>% filter(targetContrast == 0, nontargetContrast == 1, Validity==3, Target==2)
swap_TANPT2N <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TANPT2N)
```
## T2 I
```{r swap TANP T2 I}
d <- data 
dt <- d %>% filter(targetContrast == 0, nontargetContrast == 1, Validity==2, Target==2)
swap_TANPT2I <-t.test(dt$twoIncorrect, mu=50) 
report(swap_TANPT2I)
```


